---
title: "CALM1 EVAL.R"
author: "Changhua Yu"
date: "4/2/2019"
output: html_document
---
# A demo for CALM1 Submission evaluation package
```{r echo=T, results='hide'}
source("../GAA-EVAL.R")
```

## Read in the Experimental data provided by CAGI
```{r echo=T, results='hide'}
exp.data <- read.RealData(file = "exp_data.tsv", sep = "\t",
                             col.id = 1, col.value = 2, col.sd = 3)
head(exp.data$value)
```

## Read in the submission folders
```{r echo=T, results='hide'}
sub.data <- read.Submission.Folder(folder.name = "prediction/",col.id = 1,
                                      col.value = 2, col.sd = 3, real.data = exp.data)
sub.data = addGroup(sub.data,c(1,1,2,2,3,4,4))
```

## ScatterPlot inspection
```{r}
plot_all_scatter(real.data = exp.data, pred.data = sub.data, z.transform = TRUE)
```

## Correlation-based Evaluation
```{r}
# 1. Render coefficient value
result.cor.pearson <- eval.Correlation(real.data = exp.data, pred.data = sub.data,
                                       method = "pearson", sd.use = NA,z.transform = TRUE)
head(result.cor.pearson)
# 2. Plot Correlation
plot.Correlation(result.cor.pearson, "Pearson")
```

## RMSD-based Evaluation
```{r}
result.rmsd.density.norm <- eval.RMSD(real.data = exp.data, pred.data = sub.data,sd.use = NA, 
                      density.distance = TRUE, density.distance.adjust = TRUE, variance.normalization = TRUE)
head(result.rmsd.density.norm)
plot.RMSD(result.rmsd.density.norm, method="")

# with variance.normalization
result.rmsd <- eval.RMSD(real.data = exp.data, pred.data = sub.data,sd.use = NA, 
                      density.distance = FALSE, density.distance.adjust = FALSE, variance.normalization = FALSE)
head(result.rmsd)
plot.RMSD(result.rmsd, method="")
```


## Cut-off-based Evaluation
```{r}
result.auc.0.4 <- eval.AUC(real.data = exp.data, pred.data = sub.data, 
                           threshold = 0.4,z.transform = T)
head(result.auc.0.4$results)
plot.AUC(result.auc.0.4)
```

## Between-method Evaluation
```{r}
# for all the submission files
result.bM.spearman <-eval.Correlation.Between(real.data = exp.data, pred.data = sub.data,
                                              method = "spearman",sd.use = NA,z.transform = TRUE)
plot.Correlation.Between(result.bM.spearman$coefficient, method="Spearman")


# for best submission of each group
result.bM.spearman <-eval.Correlation.Between(real.data = exp.data, pred.data = sub.data,
                                              method = "pearson",sd.use = NA,z.transform = TRUE,grouped = TRUE)
plot.Correlation.Between(result.bM.spearman$coefficient, method="pearson")
```

## Partial-Correlation Evaluation
```{r}
result.pCor <- eval.Partial.Correlation(real.data = exp.data, pred.data = sub.data, method = "spearman")
plot.Correlation.Between(result.bM.spearman$coefficient, method="Spearman")
```

## PCA Plot
```{r}
total = cbind(real = exp.data$value,sub.data$value)
Plot.PCA(na.omit(total), labels=F, legend=TRUE) 
```

## Uniqueness Evaluation
```{r}
# uniqueness as adj.r^2 difference between total linear model and linear models without certain group
result.uniq = eval.uniqueness(real.data = exp.data, pred.data = sub.data)
result.uniq
plot.uniqueness(result.uniq, method="")
```

## Bootstrap Analysis
> For Correlation-based Evaluation, provide mean, CI, and median pval

```{r}
# 1. Render coefficient value
boot.result.cor.pearson <- eval.Correlation(real.data = exp.data, pred.data = sub.data,
                                       method = "pearson", sd.use = NA,z.transform = TRUE,boot = T)
head(boot.result.cor.pearson)
# 2. Plot Correlation
plot.Correlation(boot.result.cor.pearson, "Pearson",boot = TRUE)
```


> For RMSD-based Evaluation

```{r}
boot.result.rmsd <- eval.RMSD(real.data = exp.data, pred.data = sub.data,sd.use = NA, 
                      density.distance = F, density.distance.adjust = F, variance.normalization = T,boot = TRUE)
head(boot.result.rmsd)
plot.RMSD(boot.result.rmsd, method="",boot = TRUE)
```

> For Uniqueness Evaluation

```{r}
result.uniq = eval.uniqueness(real.data = exp.data, pred.data = sub.data,boot = TRUE)
result.uniq
plot.uniqueness(result.uniq, method="",boot = TRUE)
```

